%%&template
%\endofdump

\documentclass[11pt]{article}
%\usepackage{template}
%\useTemplateStatic[all]

\usepackage{src/template}

%! Generated with commit hash: "5d7e6b11019d60d4750675c9a8e8caafb6850e1b"
%! sha1sum of templateAll.fmt: "dd390d1959f0af285c0c64251268ebcd03631e05"
%! Repository URL: https://github.com/Emily3403/LaTeXtemplate
\usepackage{microtype}


\date{}
\useTemplate[english]

% TODO: Auto balance the spacing such that two cocktails are on the same page.

\def\ml#1{%
    \pgfmathsetmacro\result{#1 * 0.0333}%0.03814}%
    \pgfmathprintnumberto[precision=2]{\result}{\result}%
    #1 ml (\result~oz.)%
}
\def\counter{1}

% #1 = name, #2 = ingredients (pgffor), #3 = Equipment (pgffor), #4 = Method (pgffor)
\def\cocktail#1#2#3#4{
    \vspace{15pt}
    %
    \begin{center}
        {\bf#1}
    \end{center}
    \textbf{Ingredients:}
    \begin{itemize}
        \foreach \x in {#2} {%
            \item \x
        }
    \end{itemize}
    %
    \vspace{5pt}
    \textbf{Equipment: }%
    \foreach[count=\i] \x in {#3}{\ifnum\i=1\else, \fi\x}%
    %
    \vspace*{7pt}%
    \\%
    \textbf{Method:}
    \begin{enumerate}
        \foreach \x in {#4} {%
            \item \x
        }
    \end{enumerate}
    %
    \vspace{20pt}
    \newpage
}


\begin{document}

\cocktail{Tipperary}{
    \ml{60} Single pot still Irish whiskey,
    \ml{20} Sweet Vermouth,
    \ml{10} Green Chartreuse,
    2 Dashes orange bitters
}
%
{jigger, mixing glass, julep strainer, chilled coupe glass}
%
{
    Prepare your lemon twist.,
    Add all of your ingredients to your mixing glass and fill with ice.,
    Stir with barspoon by placing the back of the spoon against the inside of the glass and pushing the ice around until chilled and diluted.
}


\cocktail{Rum Monte Sour}{
    \ml{45} Amaro Montenegro,
    \ml{15} Dark rum,
    \ml{30} Lemon juice,
    \ml{5} Sugar syrup,
    10-\ml{15} Egg white,
    Orange twist to garnish
}
%
{jigger, shaker tins, hawthorn strainer, fine strainer, rocks glass, large ice block}
%
{
    {Add all ingredients to shaker tins, dry shake (without ice) to emulsify -- hold tins tightly!},
    {Add ice and shake again, then double strain over good ice in to your rocks glass}
    (using the hawthorn strainer and fine strainer).,
    {Fold twist over the top of the drink to expel the oils, then arrange in glass to garnish.}
}

\cocktail{Treacle}{
    \ml{60} Dark rum,
    \ml{10} Demerara sugar syrup,
    \ml{15} Cloudy apple juice,
    2 Dashes black walnut bitters,
    Orange twist to garnish
}
%
{jigger, mixing glass, barspoon, julep strainer, rocks glass, big block of ice}
%
{
    Prep your orange twist.,
    {Add all ingredients except the apple juice to the mixing glass, add plenty of ice
    and stir until chilled and diluted.},
    Strain over a big block of ice and float the apple juice on top.,
Give orange twist a sharp fold over the top to expel oils and drop in to garnish.}

\cocktail{Scofflaw}{
    \ml{50} Rye whiskey,
    \ml{25} Dry vermouth,
    \ml{10} Grenadine,
    \ml{15} Lemon juice,
    2 Dashes of orange bitters,
    Lemon twist to garnish,
    Good ice
}
%
{coupe glass, jigger, shaker tins, hawthorn strainer, fine strainer}
%
{Add all of the ingredients to your shaker tin.,
    Fill shaker tin full with ice.,
    Combine tins and shake until the tins become frosted.,
    {Open tins, double strain into a chilled coupe.},
    {Squeeze lemon twist to expel the citrus oil over it, add the twist to the drink.}
}


\cocktail{Mojito}{
    \ml{60} White rum,
    \ml{20} Fresh lime juice,
    \ml{20} Sugar syrup,
    6 -- 8 Mint leaves,
    Top soda water (optional),
    Crushed ice,
    Mint sprig to garnish
}
%
{jigger, barspoon, highball glass, tea towel, wooden mallet/rolling pin, bar
napkin (unless you’re making it for yourself!)}
%
{
    {Crush your ice if you don’t have a crushed ice machine to hand. Use tea towel and
    wooden mallet for this (wrap ice in tea towel, then smash).},
    Add all ingredients to glass and fill with ice to just under top of glass.,
    {    I don’t muddle -- just give the mint a gentle clap -- so as to keep the drink
    lighter and fresher, but if you do, do it gently.},
    Place barspoon in the glass and cover the top with the bar napkin.,
    {Churn through, add more ice and repeat until the glass is pretty much full and the
    mint is suspended through the drink.},
    Top with a cap of crushed ice and some soda water if you like a little spritz.,
    {Garnish with a mint sprig, and enjoy!}
}



\cocktail{Long Island Ice Tea}{
    \ml{15} Vodka,
    \ml{15} Gin,
    \ml{15} White rum,
    \ml{15} Tequila,
    \ml{15} Curacao/triple sec,
    \ml{15} Sugar syrup,
    \ml{30} Fresh lemon juice,
    Around \ml{45} Coca Cola,
    A skewered lemon wheel and cocktail cherry to garnish
}
%
{jigger, shaker tins, hawthorn strainer, highball glass}
%
{
    Add all of your ingredients except your coca cola to your shaker tins.,
    Pour the coca cola in to your serving glass.,
    {Fill your shaker tin with ice, seal and shake hard.},
    {Pop the tins open, but before you pour, add ice to your serving glass.},
    Use hawthorn strainer to hold the ice back in your tins and pour slowly over fresh
    ice -- this should create a layered effect.,
    {Garnish with your skewered lemon and cherry, and enjoy!}
}


\cocktail{Mai Thai}{
    \ml{60} Dark rum,
    \ml{25} Fresh lime juice,
    \ml{15} Triple sec or curacao,
    \ml{10} Orgeat syrup,
    5--\ml{10} Rich demerara sugar syrup,
    Spent lime husk,
    Mint sprig to garnish
}
%
{jigger, shaker tins, rocks glass (for tiki spirit!), straw}
%
{
    {Squeeze your lime juice, keeping one of the half husks.},
    {Add all of the ingredients except the mint into shaker tin.},
    {Fill your tin with ice, seal and shake as hard as you can.},
    {I like to serve this drink as a \enquote{shake and dump}, that is with no strainers. It is a no fuss beach drink, after all!},
    {Garnish to look like a tropical island, and enjoy! }
}

\cocktail{ZOMBIE}{
    \ml{25} Dark Rum,
    \ml{25} Golden Rum,
    \ml{25} Triple Sec,
    \ml{15} Lime Juice,
    \ml{40} Orange Juice,
    \ml{25} Passionfruit Puree,
    \ml{7.5} Grenadine,
    2 Dashes Angostura Bitter
}
%
{jigger, shaker tins, rocks glass, straw}
%
{
    Add all ingredients to a cocktail shaker.,
    Add ice to the mix and then shake well for around 30 seconds.,
    Strain using a hawthorn strainer into a Collins or Hi-Ball glass.,
    Garnish with mint sprig \& orange slice.
}

\cocktail{Negroni}{
    \ml{30} London Dry gin,
    \ml{30} Sweet vermouth,
    \ml{30} Campari,
    Orange twist to garnish,
    Good ice
}
%
{rocks glass, mixing glass, jigger, barspoon, julep strainer}
%
{
    {Prep twist.},
    {Add all of the ingredients to the mixing glass, fill with as much ice as possible.},
    {Stir until desired dilution.},
    {Strain over good quality ice.},
    {Squeeze the orange twist to expel the citrus oil over the drink, add the twist to
    drink.}
}

\cocktail{London Calling}{
    \ml{40} London Dry gin (Navy Strength if you can find it),
    \ml{15} Fresh lemon juice,
    \ml{15} Fino sherry,
    \ml{15} Sugar syrup,
    2 Dashes of orange bitters,
    Good ice,
    Grapefruit twist to garnish
}
%
{coupe, jigger, shaker tins, hawthorn strainer, fine strainer}
%
{
    Add all of the ingredients to your shaker tin.,
    Fill shaker tin full with ice. Combine tins and shake hard until the tins get frosted.,
    Open tins and double strain (use the hawthorn strainer to hold the ice back in the tin and pour through the fine strainer) into a chilled coupe.,
    Squeeze the grapefruit twist to expel the citrus oil over the drink then add the twist to the drink.
}

\cocktail{1934 Cosmopolitan Cocktail}{
    \ml{60} Gin,
    \ml{15} Cointreau,
    \ml{25} Lemon Juice,
    \ml{10} Raspberry Syrup,
    2 dashes of orange bitters
}
%
{jigger, shaker tins, fine strainer, chilled coupe glass}
%
{
    Shake all ingredients with ice.,
    Fine strain into chilled coupe glass.
}

\cocktail{Saturn}{
    {\ml{40} Gin},
    {\ml{15} Lemon juice, freshly squeezed},
    {\ml{15} Passion fruit syrup},
    {\ml{7} Falernum},
    {\ml{7} Orgeat syrup},
    {Garnish: Edible flower},
    {Garnish: Orange twist}
}
%
{blender (alternatively shaker tins), crushed ice, jigger, highball glass}
%
{
    Add all (non-garnish) ingredients to a blender (or shaker) with crushed ice.,
    Blend (or shake) a few seconds until smooth.,
    Pour unstrained into a Tiki mug or highball glass.,
    Garnish with an edible flower and an orange twist.
}

\cocktail{Sazerac}{
    \ml{60} Rye,
    \ml{10} Sugar syrup,
    10 -- \ml{15} Absinthe to rinse,
    4 Dashes Peychaud’s bitters,
    Lemon twist to garnish
}
%
{jigger, mixing glass, barspoon, julep strainer, small rock glass, shot glass}
%
{
    {Prepare a small coin of lemon peel.},
    {Fill serving glass with ice, add the absinthe, give a stir and leave to chill.},
    {Add all of the other ingredients to your mixing glass.},
    {Fill with ice, stir by pushing the ice around with the back of your spoon against the inside of the glass.},
    {Once chilled and diluted, strain the absinthe from the serving glass into the shot glass and discard the ice, then strain the drink into the serving glass.},
    {Fold your lemon peel sharply over the drink to expel the oils, then discard.},
    {Serve your Sazerac with the absinthe on the side (if you like!).}
}

\cocktail{Manhattan}{
    \ml{50} Rye whiskey,
    \ml{20} Sweet vermouth,
    2 Good dashes Angostura bitters,
    Orange twist,
    Good ice,
    Good quality cherry (e.g. Morello) to garnish
}
%
{chilled coupe glass, mixing glass, jigger, julep strainer, bar spoon}
%
{
    {Prep your twist (doesn’t have to be pretty, you will be discarding it).},
    {Add all ingredients to the mixing glass, fill with as much ice as possible.},
    {Stir until desired dilution.},
    {Strain into chilled coupe glass.},
    {Squeeze the orange twist to expel the citrus oil over the drink, then discard.},
    {Add your cherry to garnish, and enjoy!}
}

\cocktail{Hemingway Daiquiri}{
    \ml{60} White rum,
    \ml{15} Lime juice,
    \ml{15} Grapefruit juice,
    \ml{10} Maraschino liqueur,
    \ml{5} Sugar syrup,
    Maraschino cherry to garnish,
    Grapefruit zest to twist and discard
}
%
{shaker tins, jigger, hawthorne strainer, fine strainer, straw for tasting}
%
{
    {Add all non-garnish ingredients to shaker tins with ice.},
    {Shake hard until the tins get frosted.},
    {Taste test with straw (grapefruit is sometimes quite bitter depending on the season).},
    {Double strain into chilled coupe glass.},
    {Twist grapefruit zest over drink, then discard.},
    {Pop maraschino cherry into drink as garnish.}
}

\cocktail{Final Ward}{
    \ml{22.5} Rye whiskey,
    \ml{22.5} Green Charteuse,
    \ml{22.5} Maraschino,
    \ml{22.5} Lemon juice,
    Optional: Maraschino cherry to garnish
}
%
{jigger, shaker tins, fine strainer, chilled coupe glass}
%
{
    Combine all ingredients in a cocktail shaker.,
    Shake with ice and strain into a coupe glass.,
    (Optional) Garnish with Maraschino cherry
}

\cocktail{East India Negroni}{
    \ml{45} Dark rum,
    \ml{20} East India cream sherry,
    \ml{20} Campari,
    Orange twist to garnish
}
%
{jigger, mixing glass, barspoon, julep strainer, rocks glass, ice}
%
{
  Add all of the ingredients to your mixing glass.,
  Stir until it is chilled and diluted.,
  Strain over good ice.
  Squeeze your orange twist over the drink to expel the oils.,
  {Garnish, and enjoy!}
}

\cocktail{Royal Bermuda Yacht Club}{
    \ml{50} Rum,
    \ml{20} Fresh lime juice,
    \ml{15} Falernum,
    \ml{5} Dry Curacao,
    Lime wheel to garnish
}
%
{jigger, shaker tins, hawthorn strainer, fine strainer, coupe glass}
%
{
  Add all of your ingredients to your shaker tins and fill full with ice.,
  Seal the tins together and shake as hard as you can.,
  Double strain into coupe glass.,
  {Garnish with lime wheel, and enjoy!}
}


%\cocktail{}{
%
%}
%%
%{}
%%
%{
%

% TODO: Add Green Mamba

\end{document}

