\documentclass[../main.tex]{subfiles}

\begin{document}

    \category{Tropical Vibes}


    \cocktail{Royal Bermuda Yacht Club}{
        \ml{50} Rum,
        \ml{20} Fresh lime juice,
        \ml{15} Falernum,
        \ml{5} Dry Curacao,
        Lime wheel to garnish
    }
    {
            {Add all of your ingredients to your shaker tins and fill full with ice.},
            {Seal the tins together and shake as hard as you can.},
            {Double strain into coupe glass.},
            {Garnish with lime wheel.}
    }
    {Jigger, Shaker tins, Hawthorn strainer, Fine strainer, Coupe glass}

    \cocktailDivider

    \cocktail{Corn `n' Oil}
    {
        \ml{60} Plantation Rum,
        \ml{30} Falernum,
        \ml{10} Lime juice,
        2 dashes Angostura bitters
    }
    {
            {Shake everything with ice.},
            {Strain into rocks glass.},
            {Optionally serve with lime wedges.}
    }
    {Jigger, Shaker tins, Hawthorn strainer, Rocks glass}

    \cocktailDivider

    \cocktail{Saturn}{
            {\ml{40} Gin},
            {\ml{15} Lemon juice},
            {\ml{15} Passion fruit syrup},
            {\ml{7} Falernum},
            {\ml{7} Orgeat syrup},
            {Garnish: Orange twist}
    }
    {
            {Add all (non-garnish) ingredients to shaker with crushed ice.},
            {Shake a few seconds until smooth.},
            {Pour unstrained into highball glass.},
            {Garnish with orange twist and serve.}
    }
    {Jigger, Shaker Tins, Highball glass, Crushed ice}

    \cocktailDivider

    \cocktail{Mai Thai}{
        \ml{60} Dark rum,
        \ml{25} Fresh lime juice,
        \ml{15} Triple sec or curacao,
        \ml{10} Orgeat syrup,
        5--\ml{10} Rich demerara sugar syrup,
        Spent lime husk to garnish,
        Mint sprig to garnish
    }
    {
            {Squeeze your lime juice, keeping one of the half husks.},
            {Add all of the ingredients except mint into shaker tin. Fill with ice and shake as hard as you can.},
            {Dump unstrained into glass and garnish like a tropical island!}
    }
    {Jigger, Shaker tins, Highball glass}

    \clearpage

    \cocktail{Singapore Sling}{
        \ml{30} Gin,
        \ml{15} Cherry liqueur,
        \ml{8} Bénédictine,
        \ml{8} Cointreau,
        2 dashes of Angostura Bitters,
        \ml{100} Pineapple Juice,
        \ml{15} Lime Juice,
        \ml{10} Grenadine,
        Sparkling water to top
    }
    {
            {Pour ingredients in a shaker and dry shake it all up.},
            {Drop ice cubes in a tall Collins glass and just pour the Sling over.},
            {Top with soda water and serve.}
    }
    {Jigger, Shaker tins, Collins glass, about 4 ice blocks}

    \cocktailDivider

    \cocktail{ZOMBIE}{
        \ml{50} Dark Rum,
        \ml{25} Triple Sec,
        \ml{15} Lime Juice,
        \ml{40} Orange Juice,
        \ml{25} Passionfruit Puree,
        \ml{7.5} Grenadine,
        2 Dashes Angostura Bitter
    }
    {
            {Add all ingredients to a cocktail shaker.},
            {Add ice and shake well for around 30 seconds.},
            {Strain using a hawthorn strainer into a Collins glass.},
            {Optionally garnish with mint sprig \& orange slice}.
    }
    {Jigger, Shaker tins, Hawthorne Strainer, Highball glass}

    \cocktailDivider


    \cocktail{Mojito}{
        \ml{60} White rum,
        \ml{20} Fresh lime juice,
        \ml{20} Sugar syrup or brown sugar at bottom,
        6 -- 8 Mint leaves,
        Top soda water (optional),
        Crushed ice,
        Mint sprig to garnish
    }
    {
            {Add all ingredients to glass and fill with crushed ice to just under top of glass.},
            {Give the mint a gentle clap and put it in.},
            {Churn through with barspoon until the mint is suspended through the drink.},
            {Top with a cap of crushed ice and soda water if desired.},
            {Garnish with mint sprig.}
    }
    {Jigger, Barspoon, Highball glass, Crushed ice}

    \clearpage


\end{document}
