\documentclass[../main.tex]{subfiles}

\begin{document}

    \category{Fresh and Fruity}

    \cocktail{Treacle}{
        \ml{60} Dark rum,
        \ml{10} Demerara sugar syrup,
        \ml{15} Cloudy apple juice,
        2 Dashes walnut or Angostura bitters,
        Orange twist to garnish
    }
    {
            {Add all ingredients except the apple juice to the mixing glass, add plenty of ice and stir until chilled and diluted.},
            {Strain over a big block of ice and float the apple juice on top.},
            {Give orange twist a sharp fold over the top to expel oils and drop in to garnish.}
    }
    {Jigger, Mixing glass, Barspoon, Julep strainer, Rocks glass, Big block of ice}

    \cocktailDivider

    \cocktail{Hemingway Daiquiri}{
        \ml{60} White rum,
        \ml{15} Lime juice,
        \ml{15} Grapefruit juice,
        \ml{10} Maraschino liqueur,
        \ml{5} Sugar syrup,
        Optional: Maraschino cherry to garnish
    }
    {
            {Add all non-garnish ingredients to shaker tins with ice.},
            {Shake hard until tins get frosted.},
            {Taste test with straw, esp.\@ for grapefruit bitterness.},
            {Double strain into chilled coupe glass.},
        Optionally pop Maraschino cherry in.
    }
    {Jigger, Shaker tins, Hawthorne strainer, Fine strainer}

    \cocktailDivider

    \cocktail{1934 Cosmopolitan}{
        \ml{60} Gin,
        \ml{15} Cointreau,
        \ml{25} Lemon Juice,
        \ml{10} Raspberry Syrup,
        2 dashes of orange bitters
    }
    {
            {Shake all ingredients with ice.},
            {Fine strain into chilled coupe glass.}
    }
    {Jigger, Shaker tins, Fine strainer, Chilled coupe glass}

%    \clearpage\NoBgThispage{\thispagestyle{empty}~\clearpage}

% TODO some passion fruit drink?


\end{document}
