\documentclass[../main.tex]{subfiles}

\begin{document}

    \category{Fire and Smoke}

    \cocktail{Division Bell}{
        \ml{45} Mezcal,
        \ml{20} Aperol,
        \ml{10} Maraschino,
        \ml{25} Lime juice
    }
    {
            {Shake ingredients with ice.},
            {Double strain into coupe glass.},
            {Optionally twist grapefruit over the top in order to expel oils and use as garnish.}
    }
    {Jigger, Shaker tins, Hawthorne and Fine Strainer, Coupe glass}

    \cocktailDivider

    \cocktail{Cherry Merry}{
        \ml{45} Mezcal,
        \ml{20} Maraschino,
        \ml{15} Lemon juice,
        2 dashes Amaretto syrup
    }
    {
            {Shake ingredients with ice.},
            {Strain into coupe glass.},
            {Optionally garnish with cherry.}
    }
    {Jigger, Shaker tins, Hawthorne Strainer, Coupe glass}

    \cocktailDivider

    \cocktail{Scottish Scofflaw}{
        \ml{50} Scotch,
        \ml{25} Vermouth,
        \ml{10} Grenadine,
        \ml{15} Lemon juice,
        2 Dashes of orange bitters
    }
    {
            {Add all ingredients to shaker tin.},
            {Shake hard with ice.},
            {Double strain into a chilled coupe.},
            {Optionally squeeze lemon twist over drink to expel citrus oil, then add it to drink.}
    }
    {Jigger, Shaker tins, Hawthorn strainer, Fine strainer, Coupe glass, Good ice}

    \cocktailDivider

    \cocktail{Boulevardier}{
        \ml{40} Bourbon,
        \ml{20} Sweet Vermouth,
        \ml{20} Campari,
        Orange twist to garnish
    }
    {
            {Stir incredients in mixing glass, using as much ice as possible.},
            {Strain over ice. Optionally squeeze prepped orange twist over drink and add twist to glass.}
    }
    {Jigger, Mixing glass, Barspoon, Julep strainer, Rocks glass, Good Ice}%
    \hint{Switch bourbon for gin or mezcal to make a \textbf{Classic / Mezcal Negroni}.}

    \clearpage


\end{document}
