\documentclass[../main.tex]{subfiles}

\begin{document}

    \category{Serene Spirits}

    \cocktail{Martini}{
        \ml{60} Gin,
        \ml{5} Vermouth
    }
    {
            {Pour chilled vermouth \& gin into mixing glass. Stir with as much ice as possible.},
            {Strain into Martini glass}.
    }
    {Jigger, Mixing glass, Barspoon, Julep strainer, Chilled Martini glass}

    \hint{%
        This drink famously has many known variations.\\
        For instance, switching the gin for vodka and using a 2:1 ratio yields a \textbf{Wet Martini}.
    }

    \cocktailDivider

    \cocktail{Manhattan}{
        \ml{50} Rye whiskey,
        \ml{20} Sweet vermouth,
        2 Good dashes Angostura bitters,
        Orange twist,
        Good ice,
        Good quality cherry to garnish
    }
    {
            {Prep your twist.},
            {Add all ingredients to the mixing glass, fill with as much ice as possible.},
            {Stir until diluted, strain into chilled coupe.},
            {Squeeze the orange twist over the drink, then discard. Add cherry to garnish.}
    }
    {Jigger, Mixing glass, Barspoon, Julep strainer, Chilled coupe glass}

    \cocktailDivider

    \cocktail{Old Fashioned}{
        \ml{60} Rye whiskey,
        \ml{8} Sugar syrup,
        2 good dashes of Angostura bitters,
        Lemon twist
    }
    {
        Prep your twist.,
            {Add ingredients to mixing glass, fill with as much ice as possible and stir.},
            {Strain over good quality ice.}
            {Squeeze the lemon twist over drink, then insert twist.}
    }
    {Jigger, Mixing glass, Barspoon, Julep strainer, Rocks glass}

    \clearpage

    \cocktail{Vieux Carré}{
        \ml{30} Rye whiskey,
        \ml{30} Cognac,
        \ml{30} Red Vermouth,
        \ml{7} Bénédictine,
        2 dashes Peychaud's Bitters
    }
    {
        Stir all ingredients with ice until chilled and diluted.,
        Double strain into rocks glass on a large ice block.
    }
    {Jigger, Mixing glass, Barspoon, Fine Strainer, Julep strainer, Rocks glass, Ice Block}

    \cocktailDivider

    \cocktail{Sazerac}{
        \ml{60} Rye whiskey,
        \ml{10} Sugar syrup,
        \ml{15} Absinthe to rinse,
        4 Dashes Peychaud’s bitters
    }
    {
            {Fill serving glass with ice, add the absinthe, give a stir and leave to chill.},
            {Add all other ingredients to mixing glass.},
            {Fill with ice, stir by pushing the ice around with back of your spoon against the inside of the glass.},
            {Once chilled and diluted, strain the absinthe from the serving glass into the shot glass.
        Discard the ice, then strain the drink into the serving glass.},
            {Serve Sazerac with absinthe on the side.}
    }
    {Jigger, Mixing glass, Barspoon, Julep strainer, Rock glass, Shot glass}

    \clearpage


\end{document}
