\documentclass[../main.tex]{subfiles}

\begin{document}

    \category{Highballing}

    \cocktail{Vodka Fizz}{
        \ml{40} Vodka,
        \ml{20} Sugar syrup,
        \ml{20} Lemon juice,
        \ml{200} Soda water
    }
    {
            {Fill a shaker with ice cubes.},
            {Add Vodka, Lemon juice, and syrup.},
            {Shake and strain into a glass with ice.},
            {Top up with soda water.}
    }
    {}%
    \hint{Swap vodka for gin to obtain a \textbf{Gin Fizz}.}

    \cocktailDivider

    \cocktail{Moscow Mule}{
        \ml{40} Vodka,
        \ml{80} Ginger Beer,
        \ml{10} Lime juice,
        Mint as optional garnish
    }
    {
            {Fill vodka, ice and lime juice in cup.},
            {Pour ginger beer on top.},
            {Garnish with gently clapped mint.}
    }
    {}

    \cocktailDivider

    \cocktail{Wildberry Lillet}{
        \ml{30} Lillet,
        \ml{75} Wildberry soda,
        Frozen mixed fruits
    }
    {
            {Put fruits and ice in glass.},
            {Fill with Lillet and Wildberry.}
    }
    {}

    \cocktailDivider

    \cocktail{Gin Tonic}{
        \ml{30} Gin,
        \ml{60} Tonic water
    }
    {
            {Fill both ingredients in glass with ice}.
    }
    {}

    \cocktailDivider

    \cocktail{Whiskey Tonic}{
        \ml{30} Whiskey,
        \ml{5} Lime juice,
        \ml{60} Tonic water,
        Optionally lime wedge as garnish
    }
    {
            {Fill whiskey and lime juice in glass with ice.},
            {Pour tonic on top and stir gently.},
            {Optionally garnish with lime wedge(s).}
    }
    {}

    \cocktailDivider

    \cocktail{Dark `n' Stormy}{
        \ml{30} Dark rum,
        \ml{60} Ginger Beer,
        \ml{8} Lime juice,
        Optionally lime wedge as garnish
    }
    {
            {Pour dark rum into glass with ice.},
            {Top with ginger beer, then add lime juice.},
            {Gently stir to combine, optionally garnish with lime wedge.}
    }
    {}

    \clearpage

    \cocktail{Americano}{
        \ml{30} Campari,
        \ml{30} Sweet vermouth,
        \ml{120} Soda water,
        Optional lime wedge as garnish
    }
    {
            {Stir Campari and vermouth together in a glass with ice.},
            {Fill up with soda water and optionally garnish.}
    }
    {}

    \cocktailDivider

    \cocktail{Floradora}{
        \ml{60} Gin,
        \ml{15} Rasberry sirup or Chambord,
        \ml{15} Lime juice,
        \ml{90} Ginger Beer
    }
    {
            {Pour gin, rasberry sirup (or liqueur) and lime juice in glass with ice.},
            {Stir until diluted, then fill up with ginger beer.}
    }
    {}

    \cocktailDivider

    \cocktail{Stone Cold Larceny}{
        \ml{45} Bourbon,
        \ml{30} Apple juice,
        \ml{90} Ginger beer
    }
    {
            {Pour bourbon and apple juice in glass with ice.},
            {Stir until diluted, then fill up with ginger beer.}
    }
    {}

    \cocktailDivider

    \cocktail{Hemingway}{
        \ml{60} White rum,
        \ml{15} Lime juice,
        \ml{45} Grapefruit juice,
        \ml{8} Maraschino liqueur,
        Soda water to top
    }
    {
            {Fill glass with (crushed) ice.},
            {Pour in main ingredients, then stir gently.},
            {Top with soda water.},
            {Alternatively this drink call also be shaken to fully disperse the lime flavour.}
    }
    {}

    \cocktailDivider

    \cocktail{Alabama Slammer}{
        \ml{30} Bourbon,
        \ml{30} Gin,
        \ml{20} Amaretto sirup,
        \ml{90} Orange juice,
        Optional orange wheel as garnish
    }
    {
        Fill all ingedients in a glass with ice and stir heavily.,
        Optionally garnish with orange wheel and/or cocktail cherry.
    }
    {}

    \clearpage


\end{document}
