\documentclass[../main.tex]{subfiles}

\begin{document}

\clearpage
\category{Enlivening Experiences}

\cocktail{Final Ward}{
    \ml{22.5} Rye whiskey,
    \ml{22.5} Green Charteuse,
    \ml{22.5} Maraschino,
    \ml{22.5} Lemon juice,
    Optional: Maraschino cherry to garnish
}
{Jigger, Shaker tins, Fine strainer, Chilled coupe glass}
{
    Combine all ingredients in cocktail shaker.,
    {Shake with ice, strain into coupe glass.},
    Optionally garnish with Maraschino cherry.
}

\cocktailDivider

\cocktail{Eastern Bramble}{
    \ml{50} Gin,
    \ml{30} Lime Juice,
    \ml{15} Chambord,
    \ml{15} Yuzu sirup,
    \ml{15} Egg White
}
{Rocks glass, Good Ice, Jigger, Shaker tins, Hawthorn strainer, Fine strainer}
{
    {Add all ingredients to a shaker tin.},
    {First dry shake hard to get a nice froth.},
    {Then shake with ice and double strain over good quality ice.}
}

\cocktailDivider

\cocktail{Thyme of my Life}{
    \ml{45} Thyme and black tea infused gin,
    \ml{20} St.\@ Germain,
    \ml{20} Lemon juice,
    \ml{10} Sugar sirup
}
{Rocks glass, Ice cubes, Jigger, Shaker tins, Hawthorn strainer, Fine strainer}
{
    {Add all ingredients to shaker tin with ice.},
    {Shake hard and strain over ice cubes into glass.}
}

\cocktailDivider

\cocktail{Gin Basil Smash}{
    \ml{60} Gin,
    \ml{20} Lemon juice,
    \ml{10} Sugar sirup,
    10 fresh basil leaves
}
{Collins glass, Jigger, Shaker tins, Hawthorn strainer, Fine strainer}
{
    {Cut the basil into small pieces.},
    {Shake everything with ice.},
    {Double strain into glass with ice cubes.}
}

\pagebreak

\cocktail{Pornstar Martini}{
    \ml{45} (Vanilla-infused) vodka,
    \ml{20} Passion fruit sirup,
    \ml{15} Lime juice,
    \ml{15} Vanilla sirup,
    \ml{60} Chilled sparkling wine,
    Optionally passion fruit slice as garnish
}
{Chilled coupe glass, Jigger, Shaker tins, Hawthorn strainer, Fine strainer}
{
    {Shake hard all ingredients except sparkling wine with ice.},
    {Double strain into chilled coupe.},
    {Serve sparkling wine on the side and optionally garnish with slice of passion fruit.}
}

\cocktailDivider

\cocktail{Fleur de Paradis}{
    \ml{60} Gin,
    \ml{22.5} St-Germain,
    \ml{30} Grapefruit juice,
    \ml{30} Lemon juice,
    \ml{15} Simple syrup,
    1 Dash orange bitters,
    Chilled sparking wine to top
}
{Chilled coupe glass, Jigger, Shaker tins, Hawthorn strainer, Fine strainer}
{
    {Shake hard everything except sparkling wine with ice.},
    {Double strain into chilled coupe.},
    {Top with sparkling wine.}
}

\cocktailDivider

\cocktail{Ruby}{
    \ml{45} Vodka,
    \ml{22.5} St-Germain,
    \ml{30} Aperol,
    \ml{22.5} Lemon juice,
    \ml{22.5} Ruby red grapefruit juice,
    1 tablespoon egg white
}
{Chilled coupe glass, Jigger, Shaker tins, Hawthorn strainer}
{
    {First dry shake hard all ingredients (without ice).},
    {Then shake again with ice.},
    {Strain into chilled coupe.}
}

\end{document}
