\documentclass[../main.tex]{subfiles}

\begin{document}
\pagenumbering{arabic}

\category{Fire and Smoke}

\cocktail{Division Bell}{
    \ml{45} Mezcal,
    \ml{20} Aperol,
    \ml{10} Maraschino,
    \ml{25} Lime juice
}
{Coupe glass, Jigger, Shaker tins, Hawthorne and Fine Strainer}
{
    {Shake ingredients with ice.},
    {Double strain into coupe glass.},
    {Optionally twist grapefruit over the top in order to expel oils and use as garnish.}
}

\cocktailDivider

\cocktail{Cherry Merry}{
    \ml{45} Mezcal,
    \ml{20} Maraschino,
    \ml{15} Lemon juice,
    2 dashes Amaretto syrup
}
{Coupe glass, Jigger, Shaker tins, Hawthorne Strainer}
{
    {Shake ingredients with ice.},
    {Strain into coupe glass.},
    {Optionally garnish with cherry.}
}

\cocktailDivider

\cocktail{Scottish Scofflaw}{
    \ml{50} Scotch,
    \ml{25} Vermouth,
    \ml{10} Grenadine,
    \ml{15} Lemon juice,
    2 Dashes of orange bitters
}
{Coupe glass, Jigger, Shaker tins, Hawthorn strainer, Fine strainer, Good ice}
{
    Add all ingredients to shaker tin.,
    {Shake hard with ice.},
    {Double strain into a chilled coupe.},
    {Optionally squeeze lemon twist over drink to expel citrus oil, then add it to drink.}
}

\cocktailDivider

\cocktail{Boulevardier}{
    \ml{40} Bourbon,
    \ml{20} Sweet Vermouth,
    \ml{20} Campari,
    Orange twist to garnish
}
{Rocks glass, Mixing glass, Jigger, Barspoon, Julep strainer, Good Ice}
{
    {Stir incredients in mixing glass, using as much ice as possible.},
    {Strain over ice. Optionally squeeze prepped orange twist over drink and add twist to glass.}
}

\medskip
\begin{center}
    \textit{Switch bourbon for gin or mezcal and use equal parts to make a \textbf{Classic / Mezcal Negroni}.}
\end{center}


\end{document}
