\documentclass[../main.tex]{subfiles}

\begin{document}

\clearpage
\category{Fresh and Fruity}

\cocktail{Treacle}{
	\ml{60} Dark rum,
	\ml{10} Demerara sugar syrup,
	\ml{15} Cloudy apple juice,
	2 Dashes walnut or Angostura bitters,
	Orange twist to garnish
}
%
{Jigger, Mixing glass, Barspoon, Julep strainer, Rocks glass, Big block of ice}
%
{
	{Add all ingredients except the apple juice to the mixing glass, add plenty of ice and stir until chilled and diluted.},
	{Strain over a big block of ice and float the apple juice on top.},
	{Give orange twist a sharp fold over the top to expel oils and drop in to garnish.}
}

\cocktailDivider

\cocktail{Hemingway Daiquiri}{
    \ml{60} White rum,
    \ml{15} Lime juice,
    \ml{15} Grapefruit juice,
    \ml{10} Maraschino liqueur,
    \ml{5} Sugar syrup,
    Optional: Maraschino cherry to garnish
}
{Shaker tins, Jigger, Hawthorne strainer, Fine strainer, Straw for tasting}
{
    {Add all non-garnish ingredients to shaker tins with ice.},
    {Shake hard until tins get frosted.},
    {Taste test with straw, esp.\@ for grapefruit bitterness.},
    {Double strain into chilled coupe glass.},
    Optionally pop Maraschino cherry in.
}

\cocktailDivider

\cocktail{1934 Cosmopolitan}{
    \ml{60} Gin,
    \ml{15} Cointreau,
    \ml{25} Lemon Juice,
    \ml{10} Raspberry Syrup,
    2 dashes of orange bitters
}
{Jigger, Shaker tins, Fine strainer, Chilled coupe glass}
{
    Shake all ingredients with ice.,
    Fine strain into chilled coupe glass.
}

% TODO some passion fruit drink?


\end{document}
