\documentclass[../main.tex]{subfiles}

\begin{document}

\category{Serene Spirits}

\cocktail{Manhattan}{
	\ml{50} Rye whiskey,
	\ml{20} Sweet vermouth,
	2 Good dashes Angostura bitters,
	Orange twist,
	Good ice,
	Good quality cherry (e.g. Morello) to garnish
}
{
	chilled coupe glass, mixing glass, jigger, julep strainer, bar spoon
}
{
	{Prep your twist (doesn’t have to be pretty, you will be discarding it).},
	{Add all ingredients to the mixing glass, fill with as much ice as possible.},
	{Stir until desired dilution.},
	{Strain into chilled coupe glass.},
	{Squeeze the orange twist to expel the citrus oil over the drink, then discard.},
	{Add your cherry to garnish, and enjoy!}
}

\cocktailDivider

\cocktail{Old Fashioned}{
	\ml{60} Rye whiskey,
	\ml{5--10} Sugar syrup,
	2 good dashes of Angostura bitters,
	Lemon twist,
	Ice
}
{
	Rocks glass, Mixing glass, Jigger, Barspoon, Julep strainer
}
{
	Prep your twist,
	{Add bitters, rye and sugar syrup to the glass, fill with as much ice as possible and stir until desired dilution.}
		{Strain over good quality ice, squeeze the lemon twist to expel the citrus oil over the drink then add the twist to the glass. Enjoy!}
}

\newpage

\cocktail{Negroni}{
	\ml{30} London Dry gin,
	\ml{30} Sweet vermouth,
	\ml{30} Campari,
	Orange twist to garnish,
	Good ice
}
{
	Rocks glass, Mixing glass, Jigger, Barspoon, Julep strainer
}
{
	{Prep twist.},
	{Add all of the ingredients to the mixing glass, fill with as much ice as possible.},
	{Stir until desired dilution.},
	{Strain over good quality ice.},
	{Squeeze the orange twist to expel the citrus oil over the drink, add the twist to
			drink.}
}

\cocktailDivider

\cocktail{East India Negroni}{
	\ml{45} Dark rum,
	\ml{20} East India cream sherry,
	\ml{20} Campari,
	Orange twist to garnish
}
{
	jigger, mixing glass, barspoon, julep strainer, rocks glass, ice
}
{
	Add all of the ingredients to your mixing glass.,
	Stir until it is chilled and diluted.,
	Strain over good ice.
	Squeeze your orange twist over the drink to expel the oils.,
	{Garnish, and enjoy!}
}



\end{document}
