\documentclass[../main.tex]{subfiles}

\begin{document}

\clearpage
\category{Sours}

\cocktail{Whiskey Sour}{
    \ml{60} Bourbon,
    \ml{30} Lemon juice, 
    \ml{15} Sugar syrup, 
    2 dashes of orange bitters, 
    \ml{15} Egg white (optional), 
    Orange twist to garnish
}
{Rocks glass, Good Ice, Jigger, Shaker tins, Hawthorn strainer, Fine strainer}
{
    {Add all ingredients to a shaker tin. If using an egg white, add that too.},
    {First dry shake hard to get a nice froth.},
    {Then shake with ice and double strain over good quality ice.},
    {Squeeze the orange twist to expel the citrus oil over the drink then add the twist to the drink.}
}

\begin{center}
    \textit{In a similar way, \textbf{Gin Sour} and \textbf{Rum Sour} (with Angostura bitters) can be made.}
\end{center}

\cocktailDivider

\cocktail{Mezcal Sour}{
    \ml{60} Mezcal,
    \ml{30} Lime juice,
    \ml{15} Cointreau,
    \ml{15} Syrup,
    \ml{15} egg white,
    Angostura bitters for garnish
}
{Coupe glass, Good Ice, Jigger, Shaker tins, Hawthorn strainer}
{
    {Add mezcal, lime juice, Cointreau, simple syrup and egg white to a cocktail shaker without ice. Dry shake for 15 seconds.},
    {Add ice, shake again for 30 seconds.},
    {Strain drink into a cocktail glass. Garnish with a dash of bitters on the foam.}
}

\cocktailDivider

\cocktail{Rum Monte Sour}{
	\ml{45} Amaro Montenegro,
	\ml{15} Dark rum,
	\ml{30} Lemon juice,
	\ml{5} Sugar syrup,
	\ml{15} Egg white,
	Orange twist to garnish
}
%
{Jigger, Shaker tins, Hawthorn strainer, Fine strainer, Rocks glass, Large ice block}
%
{
	{Add all ingredients to shaker tins, dry shake to emulsify -- hold tins tightly!},
	{Shake again with ice, then double strain over good ice in to your rocks glass}.,
	{Fold twist over the top of the drink to expel the oils, then arrange in glass to garnish.}
}


\end{document}
