\documentclass[../main.tex]{subfiles}

\begin{document}

\category{Tropical Vibes}


\cocktail{Royal Bermuda Yacht Club}{
	\ml{50} Rum,
	\ml{20} Fresh lime juice,
	\ml{15} Falernum,
	\ml{5} Dry Curacao,
	Lime wheel to garnish
}
%
{Jigger, Shaker tins, Hawthorn strainer, Fine strainer, Coupe glass}
%
{
	Add all of your ingredients to your shaker tins and fill full with ice.,
	Seal the tins together and shake as hard as you can.,
	Double strain into coupe glass.,
	{Garnish with lime wheel.}
}

\cocktailDivider

\cocktail{Corn `n' Oil}
{
    \ml{60} Plantation Rum,
    \ml{30} Falernum,
    \ml{10} Lime juice,
    2 dashes Angostura bitters
}
{Jigger, Shaker tins, Hawthorn strainer, Rocks glass}
{
    Shake everything with ice.,
    Strain into rocks glass.,
    Optionally serve with lime wedges.
}

\cocktailDivider

\cocktail{Saturn}{
        {\ml{40} Gin},
        {\ml{15} Lemon juice},
        {\ml{15} Passion fruit syrup},
        {\ml{7} Falernum},
        {\ml{7} Orgeat syrup},
        {Garnish: Orange twist}
}
{Shaker Tins, Crushed ice, Jigger, Highball glass}
{
    Add all (non-garnish) ingredients to shaker with crushed ice.,
    Shake a few seconds until smooth.,
    Pour unstrained into highball glass.,
    Garnish with orange twist and serve.
}

\cocktailDivider

\cocktail{Mai Thai}{
    \ml{60} Dark rum,
    \ml{25} Fresh lime juice,
    \ml{15} Triple sec or curacao,
    \ml{10} Orgeat syrup,
    5--\ml{10} Rich demerara sugar syrup,
    Spent lime husk to garnish,
    Mint sprig to garnish
}
{}
{
        {Squeeze your lime juice, keeping one of the half husks.},
        {Add all of the ingredients except mint into shaker tin. Fill with ice and shake as hard as you can.},
        {Dump unstrained into glass and garnish like a tropical island!}
}

\newpage

\cocktail{Singapore Sling}{
    \ml{30} Gin,
    \ml{15} Cherry liqueur,
    \ml{8} Bénédictine,
    \ml{8} Cointreau,
    2 dashes of Angostura Bitters,
    \ml{100} Pineapple Juice,
    \ml{15} Lime Juice,
    \ml{10} Grenadine,
    Sparkling water to top
}
{Shaker tins, Jigger, Collins glass, about 4 ice blocks}
{
    {Pour ingredients in a shaker and dry shake it all up.},
    {Drop ice cubes in a tall Collins glass and just pour the Sling over.},
    {Top with soda water and serve.}
}

\cocktailDivider

\cocktail{ZOMBIE}{
    \ml{50} Dark Rum,
    \ml{25} Triple Sec,
    \ml{15} Lime Juice,
    \ml{40} Orange Juice,
    \ml{25} Passionfruit Puree,
    \ml{7.5} Grenadine,
    2 Dashes Angostura Bitter
}
{Jigger, Shaker tins, Rocks glass}
{
    Add all ingredients to a cocktail shaker.,
    Add ice and shake well for around 30 seconds.,
    Strain using a hawthorn strainer into a Collins glass.,
    Optionally garnish with mint sprig \& orange slice.
}

\cocktailDivider


\cocktail{Mojito}{
    \ml{60} White rum,
    \ml{20} Fresh lime juice,
    \ml{20} Sugar syrup or brown sugar at bottom,
    6 -- 8 Mint leaves,
    Top soda water (optional),
    Crushed ice,
    Mint sprig to garnish
}
%
{Jigger, Barspoon, Highball glass, Crushed ice}
%
{
    Add all ingredients to glass and fill with crushed ice to just under top of glass.,
    {Give the mint a gentle clap and put it in.},
    {Churn through with barspoon until the mint is suspended through the drink.},
    Top with a cap of crushed ice and soda water if desired.,
    {Garnish with mint sprig.}
}




\end{document}
